\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Fiza Sehar & 8\\
Moly Mikhail & 9\\
Francine Bulaclac & 9\\
Dhruv Sardana & 8\\
Nawaal Fatima & 6\\
\bottomrule
\end{tabular}
\end{table}

Fiza was unable to attend a team meeting due to having a migraine. Dhruv was unable to attend as he
had a conflict with a lecture. 

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } 

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Fiza Sehar & 1\\
Moly Mikhail & 1\\
Francine Bulaclac & 1\\
Dhruv Sardana & 1\\
Nawaal Fatima & 0\\
\bottomrule
\end{tabular}
\end{table}

Dhruv had two additional meetings with our supervisor regarding user testing.

\section{Lecture Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Fiza Sehar & 0\\
Moly Mikhail & 1\\
Francine Bulaclac & 1\\
Dhruv Sardana & 0\\
Nawaal Fatima & 0\\
\bottomrule
\end{tabular}
\end{table}


\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Fiza Sehar & 1\\
Moly Mikhail & 1\\
Francine Bulaclac & 1\\
Dhruv Sardana & 1\\
Nawaal Fatima & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 197 & 100\% \\
Fiza Sehar & 34 & 19\% \\
Moly Mikhail & 100 & 50\% \\
Francine Bulaclac & 24 & 12\% \\
Dhruv Sardana & 29 & 15\% \\
Nawaal Fatima & 10 & 5\% \\
\bottomrule
\end{tabular}
\end{table}

Moly has additional commits due to debugging issues and having to commit to see if changes fixes the issue on our live
application.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Fiza Sehar & 12 & 8 \\
Moly Mikhail & 25 & 20 \\
Francine Bulaclac & 24 & 23 \\
Dhruv Sardana & 19 & 6 \\
Nawaal Fatima & 5 & 4 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Charter Trigger Items}

After revisiting our team charter, we identified that no items were triggered in our team charter. 
\section{Additional Productivity Metrics}
\textbf{Research Subteam Contributions:}
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Research}\\
\midrule
Fiza Sehar & 1\\
Moly Mikhail & 0\\
Francine Bulaclac & 1\\
Dhruv Sardana & 0\\
Nawaal Fatima & 0\\
\bottomrule
\end{tabular}
\end{table}

Fiza completed research and testing on clip models to categorize images in order to better our model. 
Francine completed research on Flan-T5 and Quen models to polish the readability and flow of the generated alt text. \\

\noindent\textbf{AI Subteam Contributions:}
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Annotations}\\
\midrule
Dhruv Sardana & 100\\
Moly Mikhail & 200\\
\bottomrule
\end{tabular}
\end{table}

These contributions are for the additional images that the AI Subteam collected and annotated alt text for, to be used to further train our AI model. Moly and Dhruv worked extensively on collecting and annotating images to create a robust dataset for training. \\


\noindent\textbf{User Testing Contributions:}
Dhruv conducted 3 user testing sessions with a user tester. He also mmet with our supervisor to help debug during the user testing.
\end{document}