\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}
We will be presenting that it is possible to take as input an image and output semi-relevant alternative text. 
This will be done using any machine learning model. We will also demonstrate that its possible to build a user interface that is tabbable.
This will contribute to us being able to build an accessible interface that is compatible with screen readers. 


\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 13\\
Nawaal Fatima & 12\\
Casey Francine Bulaclac & 13\\
Moly Mikhail & 13\\
Fiza Sehar & 12\\
Dhruv Sardana & 13\\
\bottomrule
\end{tabular}
\end{table}
\begin{itemize}
    \item Nawaal Fatima was unable to join a team meeting due to getting her wisdom teeth removed and feeling unwell. 
\end{itemize}



\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: Jingchuan Sui} 

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Nawaal Fatima & 4\\
Casey Francine Bulaclac & 5\\
Moly Mikhail & 4\\
Fiza Sehar & 5\\
Dhruv Sardana & 4\\
\bottomrule
\end{tabular}
\end{table}
\begin{itemize}
    \item Nawaal Fatima was unable to join a supervisor meeting due to her PC crashing.
    \item Moly Mikhail was unable to join a supervisor meeting due to a pre-existing commitment with TAing a course. 
    \item Dhruv Sardana was unable to join a supervisor meeting due to having a doctor's appointment. 
\end{itemize}

\section{Lecture Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Nawaal Fatima & 7\\
Casey Francine Bulaclac & 9\\
Moly Mikhail & 9\\
Fiza Sehar & 5\\
Dhruv Sardana & 3\\
\bottomrule
\end{tabular}
\end{table}



\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: Christopher Schankula} 

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Nawaal Fatima & 2\\
Casey Francine Bulaclac & 2\\
Moly Mikhail & 2\\
Fiza Sehar & 1\\
Dhruv Sardana & 1\\
\bottomrule
\end{tabular}
\end{table}

\begin{itemize}
   \item Fiza was unable to attend the TA meeting as she was sick. 
\end{itemize}

\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 250 & 100\% \\
Nawaal Fatima & 35 & 14\% \\
Casey Francine Bulaclac & 74 & 29.6 \% \\
Moly Mikhail & 78 & 31.2\% \\
Fiza Sehar & 16 & 6.4\% \\
Dhruv Sardana & 47 & 18.8\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Nawaal Fatima & 6 & 33 \\
Casey Francine Bulaclac & 36 & 42 \\
Moly Mikhail & 16 & 36 \\
Fiza Sehar & 6 & 21 \\
Dhruv Sardana & 8 & 31 \\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}
For CI and CD, we used Github Actions to automatically trigger a project build and will run unit tests as they are built,
whenever a commit occurs or pull requests are opened. This ensures errors are discovered as early as possible 
and that the project remains in a working state during development. 


\section{Team Charter Trigger Items}
This section is not applicable as no items from our Team charter were triggered.

\section{Additional Productivity Metrics}

An additional metric of productivity is how well a team member's work aligns with group's expectations, discussions and is consistent with previous deliverables. 
This is a metric that was recently discussed and will be used for future deliverables. 
We plan to utilize the \textbf{Revision} label to track work that has been redone by a different team member than originally assigned. 
We will only consider large revisions to be part of this metric, excluding spelling and grammar corrections. 

\end{document}