\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\section{Demo Plans}
The team will demonstrate a fully intergated system that allows users to sign up, log in, upload images and view history. The demo will showcase the following features:
\begin{itemize}
    \item User uploads an image through the frontend interface.
    \item The image is sent to the backend server via API call.
    \item The backend processes the image using the AI model to generate ALT text.
    \item The generated ALT text is sent back to the frontend and displayed to the user.
\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
Fiza Sehar & 8\\
Moly Mikhail & 8\\
Francine Bulaclac & 8\\
Dhruv Sardana & 8\\
Nawaal Fatima & 8\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } Jingchuan Sui

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Fiza Sehar & 4\\
Moly Mikhail & 4\\
Francine Bulaclac & 4\\
Dhruv Sardana & 4\\
Nawaal Fatima & 4\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Fiza Sehar & 0\\
Moly Mikhail & 1\\
Francine Bulaclac & 1\\
Dhruv Sardana & 0\\
Nawaal Fatima & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name:} Chris Schankula

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{TA Meetings}\\
\midrule
Total & 1\\
Fiza Sehar & 1\\
Moly Mikhail & 1\\
Francine Bulaclac & 1\\
Dhruv Sardana & 1\\
Nawaal Fatima & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 394 & 100\% \\
Moly Mikhail & 84 & 21.3\% \\
Fiza Sehar & 101 & 25.6\% \\
Francine Bulaclac & 77 & 19.5\% \\
Dhruv Sardana & 112 & 28.4\% \\
Nawaal Fatima & 20 & 5.1\% \\
\bottomrule
\end{tabular}
\end{table}

AI Subteam: Francine and Fiza were working on testing, labelling and training custom data on a given model. Nawaal was working on huge model testing with larger datasets. Due to restrictions on model size, most of her work could not be regularly commited to the repository. 
For unknown reasons Shubh2294 was authored commits that were Nawaal's so we added that to her total number of commits. 
\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Moly Mikhail & 41 & 36 \\
Fiza Sehar & 29 & 22 \\
Francine Bulaclac & 34 & 28 \\
Dhruv Sardana & 41 & 36 \\
Nawaal Fatima & 12 & 7 \\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}

For CI/CD we implemented two extra workflows, backend and frontend which runs on every commit that is pushed in every branch. Each workflow uses linter tools to check for coding standards, checks for installed dependencies for backend and frontend and runs unit tests. The backend workflow has Github Secrets embedded which makes it easier to have environment variables.\\

\section{Team Charter Trigger Items}

After revisiting our team charter, we identified that no items were triggered in our team charter. 
\section{Additional Productivity Metrics}
\textbf{Research Subteam Contributions:}
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Research}\\
\midrule
Fiza Sehar & 1\\
Moly Mikhail & 1\\
Francine Bulaclac & 1\\
Dhruv Sardana & 1\\
Nawaal Fatima & 14\\
\bottomrule
\end{tabular}
\end{table}

The productivity metric reflects research that was done by team members to better understand concepts and technologies needed for the project. These are tracked through issues labelled as \texttt{research} in our issue tracker.\\

\noindent\textbf{AI Subteam Contributions:}
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Annotations}\\
\midrule
Fiza Sehar & 242\\
Francine Bulaclac & 292\\
Nawaal Fatima & 192\\
\bottomrule
\end{tabular}
\end{table}

These contributions are the images that the AI Subteam collected and annotated ALT text for, to be used as training data for our AI model. Fiza, Francine and Nawaal worked extensively on collecting and annotating images to create a robust dataset for training. \\

\noindent\textbf{Backend Subteam Contributions:}
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student}\\
\midrule
Dhruv Sardana \\
Moly Mikhail \\
Francine Bulaclac \\
\bottomrule
\end{tabular}
\end{table}

Moly and Dhruv mainly worked on development of the frontend and backend codebase. 
They both created the initial structure of the codebase and implemented various functionalities to ensure smooth operation.
All of them worked on a number of 9 fully functional APIs and have extensively contributed to the project's development.

\end{document}