\textbf{Nawaal Fatima - Development Plan Reflection}
\begin{enumerate}
    \item  \textbf{Why is it important to create a development plan prior to starting the
    project?} \newline
    Our project is very user-oriented and has more risks when it comes to reliability and functionality as Group 22 is designing for a demographic with which we have little/no working experience with.
    Knowing this, it is very important to have a blueprint of what we are bulding before we waste resources and cause our testers/end-users any unnecessary frustration. 
    When we have a plan, we can also make sure that we are all working towards the same goal. It also helps us to identify potential challenges and risks early on, allowing us to develop strategies to mitigate them.
    The development plan asked a couple questions we did't consider, which helped us to think more critically about our project and how we can make it successful.
    
    \item \textbf{In your opinion, what are the advantages and disadvantages of using
    CI/CD?} \newline
    I think there are more advantages than disadvantages when it comes to CI/CD.
    The main advantage is that it allows for faster and more frequent releases, which can lead to quicker feedback from users and a more responsive development process.
    It also helps to catch bugs and issues early in the development process, which can save time and resources in the long run.
    However, one disadvantage is that it can be difficult to set up and maintain, especially for smaller teams or projects with limited resources.
    It also requires a certain level of discipline and commitment from the development team to ensure that code is properly tested and reviewed before being merged into the main branch.
    Overall, I think the benefits of CI/CD outweigh the challenges, and it is a valuable practice for modern software development.

    \item \textbf{What disagreements did your group have in this deliverable, if any,
    and how did you resolve them?}\newline
    We're in agreement about most aspects of the development plan. Most `disagreements' we had were minor - such as naming conventiones to follow or what processes to esablish to ensure everything remains organized.
    We resolved these disagreements through open communication, making sure to listen to each other's perspectives and find solutions that worked for everyone.
    I imagine as we continue to work together, we may have more disagreements, but I am confident that we will be able to resolve them in a similar manner.
\end{enumerate}
