\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage[table]{xcolor}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations or acronyms -- you can reference the SRS tables if needed}

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document ...

\section{Functional Requirements Evaluation}

\section{Nonfunctional Requirements Evaluation}

The following section outlines the evaluation of the system tests created for the 
nonfunctional requirements. 

\newcounter{nfrtestcase}
\newcommand{\nfrtestcount}{\stepcounter{nfrtestcase}\thenfrtestcase}

% Start numbering at 15
\setcounter{nfrtestcase}{14}

\begin{longtable}{@{}c
    >{\raggedright\arraybackslash}p{4.0cm}
    >{\raggedright\arraybackslash}p{3.6cm}
    >{\raggedright\arraybackslash}p{3.6cm}
    >{\centering\arraybackslash}p{1.2cm}@{}}
  \toprule
  \textbf{ID} & \textbf{Action} &
  \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\
  \midrule
  \endfirsthead

  \multicolumn{5}{l}{\textit{(Continued from previous page)}} \\
  \toprule
  \textbf{ID} & \textbf{Action} &
  \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\
  \midrule
  \endhead

  \multicolumn{5}{r}{\textit{Continued on next page}} \\
  \endfoot

  \bottomrule
  \caption{System Tests Non-Functional Requirements Evaluation}
  \label{table:NFR-ST-eval}
  \endlastfoot


  NFR-ST\nfrtestcount & Test device and browser compatibility &
  System runs correctly on supported operating systems and browsers &
  All assertions pass &
  \cellcolor{green}Pass \\ \midrule

  NFR-ST\nfrtestcount & Evaluate alt text accuracy metrics &
  Generated alt text meets sufficiency, length, and usability thresholds &
  All assertions pass &
  \cellcolor{green}Pass \\ \midrule

  NFR-ST\nfrtestcount & Verify image privacy protection &
  Uploaded images are deleted after processing and not permanently stored &
  All assertions pass &
  \cellcolor{green}Pass \\ \midrule

  NFR-ST\nfrtestcount & Check for biased or offensive alt text &
  Generated alt text contains no harmful, biased, or inappropriate content &
  All assertions pass &
  \cellcolor{green}Pass \\ \midrule

  NFR-ST\nfrtestcount & Perform WCAG accessibility audit &
  Interface satisfies WCAG 2.1 accessibility guidelines &
  All assertions pass &
  \cellcolor{green}Pass \\ \midrule

  NFR-ST\nfrtestcount & Test screen reader compatibility &
  Screen readers correctly read generated alt text &
  All assertions pass &
  \cellcolor{green}Pass \\ \midrule

  NFR-ST\nfrtestcount & Test supported image formats &
  System successfully processes JPG, JPEG, and PNG images &
  All assertions pass &
  \cellcolor{green}Pass \\

\end{longtable}
	
\section{Comparison to Existing Implementation}	

This section will not be appropriate for every project.

\section{Unit Testing}

\section{Changes Due to Testing}

\wss{This section should highlight how feedback from the users and from 
the supervisor (when one exists) shaped the final product.  In particular 
the feedback from the Rev 0 demo to the supervisor (or to potential users) 
should be highlighted.}

\section{Automated Testing}
		
\section{Trace to Requirements}
		
\section{Trace to Modules}		

\section{Code Coverage Metrics}

\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?
  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV?  If there were
  differences, what changes required the modification in the plan?  Why did
  these changes occur?  Would you be able to anticipate these changes in future
  projects?  If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality?  (It is expected that most
  teams will have had to deviate from their original VnV Plan.)
\end{enumerate}

\end{document}